A new tidy data structure to support exploration and modeling of temporal data

### 2019-02-04 main.Rmd
prune a couple of sentences

A variable number of time representations can be spotted in the wild. A date-time object, universally accepted across computing systems, is the most commonly used type for representing time. Date-time also typically associates with a time zone including adjustments such as summer time. This diversity and time zone is acknowledged and accommodated by tsibble's index. Whist creating a tsibble, time indices are arranged from past to future within each series for the strict temporal ordering that is assumed by time series operations.

@@

There has been a long history of pipeline discussions and implementation centering around data in various aspects. A data pipeline describes the general flow of data through an analysis, and can generally assist in conceptualizing the process as it might be applied to a variety of problems. @unix coined the term "pipelines" in software development while developing Unix at Bell Labs. In Unix-based computer operating systems, a pipeline chains together a series of operations on the basis of their standard streams, so that the output of each program becomes the input to another. The Extract, Transform, and Load (ETL) process from recent data warehousing literature dating back to @kimball2011data outlines the workflow to prepare data for analysis, and can also be considered a data pipeline. @viewing-pipeline describes a viewing pipeline for interactive statistical graphics, that takes control of the transformation from data to plot. @xgobi, @ggobi, @orca, @plumbing and @xie2014reactive implemented data pipelines for the interactive statistical software **XGobi**, **GGobi**, **Orca**, **plumbr** and **cranvas**, respectively. The pipeline is typically described with a one way flow, from data to plot. For interactive graphics, where all plots need to be updated when a user interacts with one plot, the events typically trigger the data pipeline to be run. @xie2014reactive uses a reactive programming framework, to implement the pipeline, in which user's interactions trigger a sequence of modules to update their views, that is, practically the same as running the data pipeline producing each plot.

Building a data pipeline can be technically difficult to make it sufficiently general for a variety of data, with many implementation decisions to be made about the interface, input and output objects and functionality. The tidy data abstraction lays a pipeline infrastructure for data analysis modules of transformation, visualization and modeling. Each module communicates with the others, requiring tidy input, producing tidy output, chaining a series of operations together to accomplish the analytic tasks.

>>>>

A variable number of time representations can be spotted in the wild. A date-time object, universally accepted across computing systems, is the most commonly used type for representing time. Date-time also typically associates with a time zone including adjustments such as summer time. This diversity and time zone is acknowledged and accommodated by tsibble's index. When creating a tsibble, time indices are arranged from past to future within each series for the strict temporal ordering that is assumed by time series operations.

@@

A data pipeline describes the general flow of data through an analysis, and can generally assist in conceptualizing the process as it might be applied to a variety of problems. @unix coined the term "pipelines" in software development while developing Unix at Bell Labs. In Unix-based computer operating systems, a pipeline chains together a series of operations on the basis of their standard streams, so that the output of each program becomes the input to another. The Extract, Transform, and Load (ETL) process from recent data warehousing literature dating back to @kimball2011data outlines the workflow to prepare data for analysis, and can also be considered a data pipeline. @viewing-pipeline describes a viewing pipeline for interactive statistical graphics, that takes control of the transformation from data to plot. @xgobi, @ggobi, @orca, @plumbing and @xie2014reactive implemented data pipelines for the interactive statistical software **XGobi**, **GGobi**, **Orca**, **plumbr** and **cranvas**, respectively. The pipeline is typically described with a one way flow, from data to plot. For interactive graphics, where all plots need to be updated when a user interacts with one plot, the events typically trigger the data pipeline to be run. @xie2014reactive uses a reactive programming framework, to implement the pipeline, in which user's interactions trigger a sequence of modules to update their views, that is, practically the same as running the data pipeline producing each plot.

Building a data pipeline is technically difficult: many implementation decisions have to be made about the interface, input and output objects and functionality. The tidy data abstraction lays the plumbing for data analysis modules of transformation, visualization and modeling. Each module communicates with the others, requiring tidy input, producing tidy output, chaining a series of operations together to accomplish the analytic tasks.
